The Evolution of Phenotypically Invariant Genetic Networks

### 2017-08-11 kalman_walk_paper.tex
started stuff on hybrid vigor

Some $F_2$s will have perfect fitness, and some will be worse off than both parents. \jss{I still need to do the calculations.} For instance if $r=1$ so that parental populations reside on the unit circle, two randomly drifted populations will create $F_1$s a distance of, on average, $0.6684$. Some $F_2$s from this population wil be back at the origin (a quarter of the time), others as far away as $\sqrt{2}$ (a quarter of the time), and some will stay a distance of $1$ away (half the time).

>>>>

Some $F_2$s will have perfect fitness, and some will be worse off than both parents. \jss{I still need to do the calculations.} For instance if $r=1$ so that parental populations reside on the unit circle circumference, two randomly drifted populations will create $F_1$s a distance of, on average, $0.6684$. Some $F_2$s from this population wil be back at the origin (a quarter of the time), others as far away as $\sqrt{2}$ (a quarter of the time), and some will stay a distance of $1$ away (half the time).
